---
title: "Master thesis data analysis"
author: "Y.Oude_Heuvel"
date: "2023-05-29"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library('Hmisc')
library('tidyverse')
library('ggplot2')
library('readxl')
```


####Reading in data for hypothesis 1
```{r}
df_adj <- read_excel("C:/Users/Yannick/OneDrive/Bureaublad/excel_ files_data_analysis/AdjustedScores.xlsx")
```

### 1. T-test for Virtual reality vs Computer-Based versions

##Cleaning data/preparing data

#Putting all 0's to NA (I counted those as exploded balloons, but for my own data i should check if they actually exploded)
```{r}
df_adj [df_adj == 0] <- NA
df_adj
```


#Removing non-numeric colums
```{r}
df_adj_2 <- df_adj[, -c(1:3)]
df_adj_2

```

#adding adjusted score 
```{r}
df_adj_3 <- df_adj_2 %>%
  add_column(Adjusted_Score = rowMeans(df_adj_2, na.rm = TRUE))
df_adj_3

```

#adding the adjusted score to the original data frame
```{r}
df_adj <- df_adj %>%
  add_column(Adjusted_Score = df_adj_3$Adjusted_Score) 

```

## actual t-test

#using summarise to get the mean and sd for adjusted score, both for CB and VR
```{r}
df_adj %>%
  group_by(Version) %>%
  summarise(mean = mean(Adjusted_Score), sd = sd(Adjusted_Score))
```
#t-test CB vs VR
```{r}
res <- t.test(Adjusted_Score ~ Version, data = df_adj, paired = TRUE)
res
```


### 2. calculating differences between cb and vr for the first, second and third sets of balloons seperately

## first cleaning and preparing the data

# making seperate dataframes for the first, second and third sets (but with both cb and vr)
```{r}
df_adj_1_10 <- df_adj [, -c(1:3, 14:34)]
df_adj_11_20 <- df_adj [, -c(1:13, 24:34)]
df_adj_21_30 <- df_adj [, -c(1:23, 34)]

df_adj_1_10
df_adj_11_20
df_adj_21_30
  
```
#calculating adjusted score

```{r}
df_adj_1_10 <- df_adj_1_10 %>%
  add_column(AdjustedScore = rowMeans(df_adj_1_10, na.rm = TRUE))

df_adj_11_20 <- df_adj_11_20 %>%
  add_column(AdjustedScore = rowMeans(df_adj_11_20, na.rm = TRUE))

df_adj_21_30 <- df_adj_21_30 %>%
  add_column(AdjustedScore = rowMeans(df_adj_21_30, na.rm = TRUE))
```


#adding back the version

```{r}
df_adj_1_10 <- df_adj_1_10 %>%
  add_column(Version = df_adj$Version)

df_adj_11_20 <- df_adj_11_20 %>%
  add_column(Version = df_adj$Version)

df_adj_21_30 <- df_adj_21_30 %>%
  add_column(Version = df_adj$Version)
```

## actual t-test

```{r}
res_24 <- t.test(AdjustedScore ~ Version, data = df_adj_1_10, paired = TRUE)
res_25 <- t.test(AdjustedScore ~ Version, data = df_adj_11_20, paired = TRUE)
res_26 <- t.test(AdjustedScore ~ Version, data = df_adj_21_30, paired = TRUE)

res_24
res_25
res_26
```

### visualization (one graph with multiple boxplots)


## more data cleaning/prepping

# adding adjusted scores for different sets to T_Adj_5

```{r}
df_adj <- df_adj %>%
  add_column(AdjustedScore1_10 = df_adj_1_10$AdjustedScore) %>%
  add_column(AdjustedScore11_20 = df_adj_11_20$AdjustedScore) %>%
  add_column(AdjustedScore21_30 = df_adj_21_30$AdjustedScore)
  

```

#removing every other column

```{r}
df_adj_score <- df_adj[, -c(1:33)]
df_adj_score
```

#putting it all in one column
```{r}
df_adj_score2 <- data.frame(AdjustedScore=unlist(df_adj_score, use.names=FALSE))
```

#making a df with condition four times

```{r}
df_adj_con <- df_adj %>%
  mutate(Version2 = df_adj$Version, Version3 = df_adj$Version, Version4 = df_adj$Version)
df_adj_con
```

```{r}
df_adj_con <- df_adj_con[, -c(1, 2, 4:37)]
df_adj_con
```

```{r}
df_adj_con <- data.frame(Condition=unlist(df_adj_con, use.names=FALSE))
df_adj_con
```

#adding a column with four different sets to T_adj_5_score2

```{r}
df_adj_score2 <- df_adj_score2 %>%
  mutate(set = c("AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "AllSets", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set1", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set2", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3", "Set3"))
```


#adding condition
```{r}
df_adj_score2 <- df_adj_score2 %>%
  mutate(Version = c(df_adj_con$Condition))
```


## actual plot

#gg plot for all difference in one plot

```{r}
plot_5 <- ggplot(df_adj_score2, aes(x=set, y=AdjustedScore, color=Version)) + geom_boxplot()

plot_5
```


#exporting it to a png file
```{r}
png("plot_5.png")
print(plot_5)
dev.off()
```

#### Reading in data for hypothesis 2 & 3

```{r}
df_q <- read_excel("C:/Users/Yannick/OneDrive/Bureaublad/excel_ files_data_analysis/QScores2.xlsx")

```


### correlation tables hyp 2

## data cleaning/prepping

#had a few missing scores, so I put them to NA
```{r}
df_q [df_q == 'NA'] <- NA
df_q
```


#making a data frame with participant ID and adjusted score over all 30 balloons
```{r}
df_adj_s_VR <- df_adj_CVR[, -c(2:33)]
  df_adj_s_VR
```

```{r}
df_adj_s_CB <- df_adj_CCB[, -c(2:33)]
df_adj_s_CB
```


#adding relevant questionnaire scores
```{r}
df_adj_q_VR <- df_adj_s_VR %>%
  mutate(BIS = df_q$BIS, EV = df_q$`E-V`, EI = df_q$`E-I`, BC = df_q$BC, BSSS = df_q$BSSS, AUDIT = df_q$Audit, Drugs = df_q$Drugs, Cigarettes = df_q$Cigarettes, Sex = df_q$Sex, Stealing = df_q$Steal, Seatbelt = df_q$Seatbelt, GABS = df_q$GABS, IPQ_CB = df_q$CBIPQ,  IPQ_VR = df_q$VRIPQ, Age = df_q$Age, Gender = df_q$Gender)
df_adj_q_VR
```

```{r}
df_adj_q_CB <- df_adj_s_CB %>%
  mutate(BIS = df_q$BIS, EV = df_q$`E-V`, EI = df_q$`E-I`, BC = df_q$BC, BSSS = df_q$BSSS, AUDIT = df_q$Audit, Drugs = df_q$Drugs, Cigarettes = df_q$Cigarettes, Sex = df_q$Sex, Stealing = df_q$Steal, Seatbelt = df_q$Seatbelt, GABS = df_q$GABS, IPQ_CB = df_q$CBIPQ,  IPQ_VR = df_q$VRIPQ, Age = df_q$Age, Gender = df_q$Gender)
df_adj_q_CB
```


## spearman correlations


```{r}
res_27 <- rcorr(as.matrix(df_adj_q_VR), type=c("spearman"))
res_27

```

```{r}
res_28 <- rcorr(as.matrix(df_adj_q_CB), type=c("spearman"))
res_28

```

### t-test for hyp 3

## more data cleaning/prepping

#making a df with just IPQ scores

```{r}
df_IPQ <- data.frame(IPQ = c(df_q[, "CBIPQ"], df_q[, "VRIPQ"] ))
```

```{r}
df_IPQ <- data.frame(IPQ=unlist(df_IPQ, use.names=FALSE))
df_IPQ
```
```{r}
df_IPQ <- df_IPQ %>%
  mutate (Version = c("CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "CB", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR", "VR"))
df_IPQ
```

## t-test and visualization

#means and sd's for IPQ (CB and VR)
```{r}
df_IPQ%>%
  group_by (Version)%>%
  summarise(mean = mean(IPQ, na.rm = TRUE), sd = sd(IPQ, na.rm = TRUE))
```

#t-test for IPQ
```{r}
res_29 <- t.test(IPQ ~ Version, data = df_IPQ, paired = TRUE)
res_29
```

#boxplot
```{r}
f2 <- ggplot(df_IPQ, aes(x = Version, y = IPQ)) +
  geom_boxplot()

f2
```


```{r}
png("f2.png")
print(f2)
dev.off()
```

#### demographic data for participants section

```{r}
df_q%>%
  summarise(mean = mean(Age, na.rm = TRUE), sd = sd(Age, na.rm = TRUE))
```


